%-------------------------
% Resume in Latex
% Author : Mahmud Zaman Bali
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
% Get rid of warnings
\setlength{\footskip}{4.08003pt}
% ATS friendly
% \input{glyphtounicode}

\usepackage{xcolor}
\hypersetup{colorlinks,urlcolor=blue}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% serif
% \usepackage{CormorantGaramond}
\usepackage{fontspec}
% Custom font
\setmainfont{Arial}
\newfontfamily{\futura}{Futura}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{gray}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
% \pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

%----------HEADING----------

\begin{tabularx}{\textwidth}{>{\raggedright\arraybackslash}X >{\centering\arraybackslash}X >{\raggedleft\arraybackslash}X}
    \href{mailto:mahmudzbali@gmail.com}{mahmudzbali@gmail.com} & \textbf{{\futura\Large Mahmud Zaman Bali}} & GitHub: \href{https://github.com/mzbali}{github.com/mzbali} \\
    Mobile: +44 7405 736719 & London, United Kingdom & LinkedIn: \href{https://www.linkedin.com/in/mzbali/}{ linkedin.com/mzbali} \\
    & \href{https://mzbali.com/}{mzbali.com} & \\
\end{tabularx}


%\begin{center}
 %   \textbf{\Huge \scshape Mahmud Zaman Bali} \\ \vspace{1pt}
 %   \small +44 7405736719 $|$ \href{mailto:mahmudzbali@gmail.com}%
 %{\underline{mahmudzbali@gmail.com}} $|$ 
   % \href{https://linkedin.com/in/mzbali}{\underline{linkedin.com/in/mzbali}} $|$
   % \href{https://github.com/mzbali}{\underline{github.com/mzbali}}
% \end{center}

%-----------SUMMARY-----------
\section{Summary}
Aspirant software developer with a MSc in Artificial Intelligence.  Proven track record in building complete web based applications and applying CI/CD practices. Seeking software development roles where I can contribute to innovative, user-focused projects. 

%-----------MISCELLANEOUS SKILLS-----------
% \section{Work Permit}

% \begin{itemize}[leftmargin=0.15in, label={}]
%   \small{\item{
%   \textbf{ No Sponsorship Required} now or in the future.} 
%   }
% \end{itemize}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Queen Mary University of London}{London, United Kingdom}
      {MSc, Artificial Intelligence}{2022 -- 2023}
      \resumeItemListStart
        \resumeItem{\textbf{1st} class \textbf{Distinction}.}
        \resumeItem{\textbf{Modules:} Natural Language Processing, Machine Learning, Applied Statistics, Deep Learning.}
      \resumeItemListEnd
    \resumeSubheading
      {American International University-Bangladesh}{Dhaka, Bangladesh}
      {BSc, Computer Science and Engineering}{2017 -- 2021}
    \resumeItemListStart
        \resumeItem{\textbf{GPA:} 3.93/4.00}
        \resumeItem{\textbf{Modules:} Software Engineering, Web Technologies, Object Oriented Programming, OOP Analysis \& Design.}
        \resumeItem{\textbf{Achievements:} Dean’s List Award.}
    \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart
  \resumeProjectHeading
    {{\textbf{JavaScript Comment Generation}} $|$ \emph{ PyTorch, Numpy, Pandas, Hugging Face, Jupyter Notebook}}{}
  \resumeItemListStart
    \resumeItem{Investigated the use of pre-trained transformer models for JavaScript code summarization tasks.}
\resumeItem{Researched and implemented state-of-the-art Natural Language Processing (NLP) techniques within the software development context.}
\resumeItem{Analysed the performance of different models using relevant evaluation metrics.}
\resumeItem{Conducted regular progress reviews with supervisor, ensuring research alignment and addressing challenges.}
  \resumeItemListEnd

  \resumeProjectHeading
    {{\textbf{BugBlitz}} $|$ \emph{ Next.js, .NET Core, PostgreSQL, Docker, Azure}}{}
  \resumeItemListStart
    \resumeItem{Developed using .NET Core 8 and Next.js by adhering to SOLID guidelines.}
\resumeItem{Devised secure authentication, built CRUD operations, improving project efficiency.}
\resumeItem{Decreased code complexity by 20\% by delegating authentication to an OAuth2 microservice.}
\resumeItem{Applied caching in Next.js, substantially cutting back on database queries and boosting efficiency.}
    \resumeItem{Deployed on Azure VM using Docker Swarm (CapRover) with HTTPS for API \& Client.}
    \resumeItem{GitHub: \href{https://github.com/mzbali/bugblitz}{https://github.com/mzbali/bugblitz}}
    \resumeItem{Website: \href{https://bugblitz.mzbali.com}{https://bugblitz.mzbali.com}}
  \resumeItemListEnd
    \resumeSubHeadingListEnd
%-----------EXPERIENCE-----------
\section{Experience}

\resumeSubHeadingListStart

\resumeSubheading
{Teaching Assistant (Computer Science)}
{Dhaka, Bangladesh}
{American International University-Bangladesh}
{2020 -- 2021}

\resumeItemListStart

\resumeItem{Developed lesson materials for CS courses, emphasising programming concepts and problem-solving.} 
\resumeItem{Provided focused tutoring to students, aiding in programming challenges and code debugging.}
\resumeItem{Designed quizzes and assessments to gauge student comprehension of core CS concepts.} 
\resumeItem{Collaborated with instructors to address student programming difficulties, promoting academic success.} 

\resumeItemListEnd


      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

  \resumeSubHeadingListEnd

%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Machine Learning:} PyTorch, Numpy, Pandas, Hugging Face, Jupyter Notebook \\
    \textbf{DevOps:} Git, Bash, Docker, GitHub Actions \\
     \textbf{Web Development:} React, Next.js, Python C\#, Typescript, JavaScript \\
    \textbf{Databases:} PostgreSQL, Redis  \\
    \textbf{Others:} Jupyter Notebook, VS Code, Pycharm, Rider, Linux, MacOS \\
    }}
 \end{itemize}
 
%-----------LANGUAGE SKILLS-----------
\section{Language Proficiency}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{English}{: Fluent (IELTS 7.5)} \\
     \textbf{Bengali}{: Native}
    }}
 \end{itemize}

%-------------------------------------------
\end{document}
